\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-04 manuscript.Rmd

## Merge "0"s and "1"s into "1"s 9select,subset assign)
descriptives.data[ , 6:53 ][ descriptives.data[ , 6:53 ] == 0 ] <- 1
EFA.descriptives <- descriptives.data[1:428,]
CFA.descriptives <- descriptives.data[429:690, ]
IRT.descriptives <- descriptives.data

@@

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam

### IRT data
IRT.data <- sem.data
IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
IRTRitem37 = recode(IRT.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
IRT.data <- IRT.data %>% 
  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
```

```{r descriptives, eval=FALSE, include=FALSE}
#Use these  data frames for descriptive
EFA.descriptives #Only EFA, n =428
CFA.descriptives #Only CFA, n =262  
IRT.descriptives# Total sample, n = 690

@@

>>>>

## Merge "0"s and "1"s into "1"s 9select,subset assign)
descriptives.data[ , 6:53 ][ descriptives.data[ , 6:53 ] == 0 ] <- 1
EFA.descriptives <- descriptives.data[1:428,]
CFA.descriptives <- descriptives.data[429:690, ]

@@

## renaming the column-header
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
```

```{r descriptives, eval=FALSE, include=FALSE}
#Use these  data frames for descriptive
EFA.descriptives #Only EFA, n =428
CFA.descriptives #Only CFA, n =262  
descriptives.data# Total sample, n = 690

@@

```{r IRT data, include=FALSE}

F1.IRT.data <- sem.data %>% 
  select(item16, item36,  item17)

F2.IRT.data <- sem.data %>% 
  select(item16, item36,  item17)

"F1 =~ item16 + item36 + item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a1*item32 +item35 + item38+ a2*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1

IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')

IRT.data <- IRT.data %>% 
  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
```
